---
title: "FMPH221 Project Report Code"
author: "Gabriel Riegner & Kevin Nguyen"
output: pdf_document
---

# Loading Libraries
```{r}
library(alr4)
library(GGally)
library(leaps)
```

# Functions
```{r}

```

# Data and key
```{r}

```

# Log transforming the skewed variables
## Chosen by a visual inspection of each histogram
```{r}

```

# Principal Component Analyses to reduce collinearity and dimensionality
## Many of the predictors are measuring the same things
```{r}

```

# Feature selection
## using in-sample criteria to maximize R^2
```{r}

```

# Pairs Plot
```{r}
ggpairs()
```

# Naive model
```{r}
ols1 = lm(siips ~ ., data = )
residualPlots(ols1) #  nonlinearity
vif(ols1) # collinearity
ncvTest(ols1) # heteroscedasticity
```

# Addressing nonlinearity: quadratic terms
```{r}

```

# Addressing collinearity: removing serotonin
```{r}

```

# Check to see if errors are autocorrelated
```{r}

```

# Bootstrap to re-estimate standard errors and t-values, under heteroscedasity
```{r}

```

# Compiling bootstrap results
```{r}

```

# Compare summary tables
```{r}

```

# Compare confidence intervals
```{r}

```

# Outliers
```{r}
plot(ols2, 4)
outlierTest(ols2)
```

# Normality of errors
```{r}
qqPlot(ols2)
```