---
title: "FMPH221 Project Report Code"
author: "Gabriel Riegner & Kevin Nguyen"
output: pdf_document
---

# Loading Libraries
```{r}
library(alr4)
library(GGally)
library(leaps)
```

# Functions
```{r}
normalize = function(x) { # used to scale data to 0 to 1 [later important for log transformation]
  (x - min(x)) / (max(x) - min(x))
}
```

# Data and key
```{r}
neuromaps_df = read.csv("data/neuromaps-mni152_y-siips_res-basc444.csv")
neuromaps_df = apply(neuromaps_df, 2, normalize) |> as.data.frame()
neuromaps_key = read.csv("data/neuromaps-key.csv")
```

# Log transforming the skewed variables
## Chosen by a visual inspection of each histogram
```{r}
logcols = c(
    "aghourian2017.feobv",
    "bedard2019.feobv",
    "gallezot2010.p943",
    "jaworska2020.fallypride",
    "sandiego2015.flb457",
    "sasaki2012.fepe2i",
    "tuominen.feobv"
)
neuromaps_df[logcols] = log(neuromaps_df[logcols] + 1)
```

# Principal Component Analyses to reduce collinearity and dimensionality
## Many of the predictors are measuring the same things
```{r}
neuromaps_pca = data.frame(siips = neuromaps_df$siips)

for (group in unique(neuromaps_key$description)) {
    colnames = neuromaps_key[neuromaps_key$description == group, "colname"]
    if (length(colnames) > 1) { # first PC
        pcs <- prcomp(neuromaps_df[, colnames])
        neuromaps_pca[, paste0(group, ".pc1")] = pcs$x[, 1]
    } else { # leave as is
        neuromaps_pca[group] = neuromaps_df[, colnames]
    }
}
```

# Feature selection
## using in-sample criteria to maximize R^2
```{r}

```

# Pairs Plot
```{r}
ggpairs()
```

# Naive model
```{r}
ols1 = lm(siips ~ ., data = )
residualPlots(ols1) #  nonlinearity
vif(ols1) # collinearity
ncvTest(ols1) # heteroscedasticity
```

# Addressing nonlinearity: quadratic terms
```{r}

```

# Addressing collinearity: removing serotonin
```{r}

```

# Check to see if errors are autocorrelated
```{r}

```

# Bootstrap to re-estimate standard errors and t-values, under heteroscedasity
```{r}

```

# Compiling bootstrap results
```{r}

```

# Compare summary tables
```{r}
summary(ols2)$coefficients |> round(3)
boot_summary |> round(3)
```

# Compare confidence intervals
```{r}
confint(ols2) |>
    cbind(t(ci)) |>
    round(3)
```

# Outliers
```{r}
plot(ols2, 4)
outlierTest(ols2)
```

# Normality of errors
```{r}
qqPlot(ols2)
```